% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{geometry}
\usepackage{hyperref}
\usepackage{multicol}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Robert Dinterman}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://robertdinterman.com/research/CV_Dinterman.pdf}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {economics, regional economics, spatial econometrics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://aede.osu.edu/home}{The Ohio State University} \\
  Department of Agricultural, \\
  Environmental, and Development \\
  Economics (AEDE) \\
  % Agricultural Administration Building \\
  2120 Fyffe Road, Room 229 \\
  Columbus, OH 43210-1067
\end{minipage}
\begin{minipage}{0.5\linewidth}
  \begin{tabular}{ll}
    % Phone: & (919) 627-8622 \\
    % Fax: &  (919) 513-5613 \\
    Email: & \href{mailto:dinterman.1@osu.edu}{\tt dinterman.1@osu.edu} \\
    Webpage: & \href{http://robertdinterman.com/}{\tt http://robertdinterman.com/} \\
  \end{tabular}
\end{minipage}


% \section*{Personal}
% 
% \begin{itemize}
% \item Born on September 29, 1895.
% \item United States Citizen.
% \end{itemize}
% 

\section*{Education}

\begin{itemize}
  \item Ph.D. Economics, North Carolina State University, 2016.
    \subitem Fields: Regional Economics, Spatial Econometrics, and Applied Econometrics
    %\subitem [Advanced level courses in Spatial Statistics]

  \item M.E. Economics, North Carolina State University, 2011.

  \item B.A. Philosophy \& Economics, Clemson University, 2008.
\end{itemize}


\section*{Employment}
\begin{itemize}
\item The Ohio State University:
\begin{itemize}
\item Post-Doctoral Researcher in Agribusiness, Department of Agricultural, Environmental, and Development Economics and \href{http://aede.osu.edu/programs/farm-income-enhancement-program}{Farm Income Enhancement Program}, 2016 -- present.
\end{itemize}
\end{itemize}

\subsection*{Research Experience}

\begin{itemize}
\item United States Department of Agriculture - Economic Research Services:
\begin{itemize}
\item Economist, Summer 2011, Summer 2012, and Summer 2014.
\end{itemize}

\item North Carolina State University, Department of Economics:
\begin{itemize}
\item Research Assistant, Chatham Park Economic Impact (Michael L. Walden), Fall 2014.
\item Research Assistant, Various Projects (Mitch Renkow), Fall 2013.
\item Research Assistant, Network Structure of Biopharmaceutical Patents (Turanay Caner), Fall 2010.
\end{itemize}

\item National Bureau of Economic Research:
\begin{itemize}
\item Research Assistant, Statistical Methods in Integrated Assessment Models (Michael J. Roberts), Summer 2010.
\end{itemize}
\end{itemize}

\subsection*{Teaching Experience}
\begin{itemize}
\item North Carolina State University, Department of Economics:
\begin{itemize}
\item Instructor, EC 495 (Topics in Sports Economics), Fall 2012.
\item Instructor, EC 351 (Introduction to Econometrics), Spring 2014 -- Summer 2014.
\item Instructor, EC 202 (Principles of Macroeconomics), Fall 2010 -- Summer 2013.
\item Teaching Assistant, EC 205 (Fundamentals of Economics), Fall 2009 -- Spring 2010.
\end{itemize}

\item Campbell University (Buies Creek, NC), Lundy-Fetterman School of Business:
\begin{itemize}
\item Lecturer, (Sports Economics, Principles of Macroeconomics), Spring 2014.
\end{itemize}
\end{itemize}

\section*{Publications}

\begin{itemize}
\item \href{https://scholar.google.com/citations?user=4e7if58AAAAJ&hl=en}{Google Scholar Profile}
\item \href{https://ageconsearch.umn.edu/search?ln=en&p=dinterman&f=&sf=&so=d&rg=10}{AgEcon Search Profile}
\end{itemize}

\subsection*{Peer Reviewed Journal Articles}
\begin{itemize}
\item \textbf{Dinterman, R.} and A.L. Katchova. ``Property Tax Incidence on Cropland Cash Rent.'' \emph{Applied Economic Perspectives and Policy}, forthcoming. \href{https://doi.org/10.1093/aepp/ppz004}{https://doi.org/10.1093/aepp/ppz004}
\item \textbf{Dinterman, R.}, A.L. Katchova, and J. Harris. ``Financial Stress and Farm Bankruptcies in U.S. Agriculture.'' \emph{Agricultural Finance Review}, 78(2018). \href{https://doi.org/10.1108/AFR-05-2017-0030}{https://doi.org/10.1108/AFR-05-2017-0030}
\item Katchova, A.L. and \textbf{R. Dinterman}. ``Evaluating Financial Stress and Performance of Beginning Farmers during the Agricultural Downturn.'' \emph{Agricultural Finance Review}, 78(2018). \href{https://doi.org/10.1108/AFR-08-2017-0074}{https://doi.org/10.1108/AFR-08-2017-0074}
\item Eyer, J., \textbf{R. Dinterman}, A. Rose, and N. Miller. ``The Effect of Disasters on Migration Destinations: Evidence from Hurricane Katrina.'' \emph{Economics of Disasters and Climate Change}, 2(2018), 91-106. \href{https://doi.org/10.1007/s41885-017-0020-3}{https://doi.org/10.1007/s41885-017-0020-3}
\item \textbf{Dinterman, R.} and M. Renkow. ``Evaluation of USDA Broadband Loan Programs: Impacts on broadband provision.'' \emph{Telecommunications Policy}, (2016). \href{https://doi.org/10.1016/j.telpol.2016.12.004}{https://doi.org/10.1016/j.telpol.2016.12.004}
\item Stenberg, P., and \textbf{R. Dinterman}. ``The Digital Economy in the Western United States,'' \emph{Rural Connections}, vol. 6, no. 1 (September 2011): 43--48.
\end{itemize}

\subsection*{Book Chapters}

\begin{itemize}
\item Pender, J., and \textbf{R. Dinterman}. ``Developing a Typology of Wealth Creation Approaches and Contexts: Hypotheses and an example for the case of attracting retirees,'' in  John L. Pender, Bruce A. Weber, Thomas G. Johnson, and J. Matthew Fannin (eds.), \emph{Rural Wealth Creation}, Taylor \& Francis, 2014: 269--290.
\end{itemize}

\subsection*{Under Review}

\begin{itemize}
\item \textbf{Dinterman, R.} and A.L. Katchova. ``Survival Analysis of Farm Bankruptcy Filings.''
\end{itemize}

\subsection*{Working Papers}

\begin{itemize}
\item \textbf{Dinterman, R.}, J. Eyer, and A.L. Katchova. ``Farm financial stress in the face of changing growing conditions.''
\item \textbf{Dinterman, R.} and A.L. Katchova. ``Farm Bankruptcies and Land Value Trends: The Effects of Land Value Fluctuations on Financial Stress.''
\item \textbf{Dinterman, R.}. ``Broadband, Local Employment, and Population Growth.''
\end{itemize}

% \subsection*{Works In Progress}
% 
% \begin{itemize}
% \item ``Analyzing the Characteristics of the Next Generation of Farmers and Ranchers: a beginning farmers and ranchers typology,'' with Ani Katchova (The Ohio State University).
% \item ``You built it, but are they coming? Analyzing the impact of Minor League Baseball teams on Rural Communities,'' with Andrew Boslett (University of Rochester).
% \item ``The Effect of High-Speed Internet on U.S. Farms: An Evaluation of the USDA Broadband Loan Program,'' with Ivan Kandilov (NC State), Mitch Renkow (NC State), Peter Stenberg (USDA-ERS).
% \item ``Measuring the Impact of Migration Flows: A Spatial Origin-to-Destination Model of Interregional Movement.''
% \end{itemize}

\subsection*{Presentations}

\begin{itemize}
\item ``Preferential Agricultural Property Tax's Impact on Land Values,'' NC-1177 Agricultural and Rural Finance Markets in Transition: Dallas, TX 8 October 2019.
\item ``Preferential Agricultural Property Tax's Impact on Land Values,'' Agricultural and Applied Economics Association (AAEA) Conference: Atlanta, GA 22 July 2019.
\item ``Farmer Bankruptcy Trends Post-2007,'' NC-1177 Agricultural and Rural Finance Markets in Transition: St Louis, MO 10 October 2018.
\item ``Farm financial stress in the face of changing growing conditions,'' NC-1177 Agricultural and Rural Finance Markets in Transition: St Louis, MO 9 October 2018.
\item ``Survival Analysis of Farm Bankruptcy Filings,'' Agricultural and Applied Economics Association (AAEA) Conference: Washington, DC 7 August 2018.
\item ``Taxation Incidence on Rented Agricultural Land: An Evaluation of Ohio's Current Agricultural Use Value Program.'' NC-1177 Agricultural and Rural Finance Markets in Transition: Minneapolis, MN 3 October 2017.
\item ``Farm Bankruptcies and Land Value Trends: The Effects of Land Value Fluctuations on Financial Stress,'' Agricultural and Applied Economics Association (AAEA) Conference: Chicago, IL 1 August 2017.
\item ``What influences the destination of disaster migrants? Evidence from Hurricane Katrina,'' Association of Environmental and Resource Economists (AERE) Annual Summer Conference: Pittsburgh, PA 2 June 2017.
\item ``Financial Stress and Farm Bankruptcies in U.S. Agriculture,'' NC-1177 Agricultural and Rural Finance Markets in Transition: Denver, CO 3 October 2016.
\item ``Broadband, Local Employment, and Population Growth,'' North American Meetings of the Regional Science (NARSC) Association International: Washington, DC 15 November 2014.
\item ``A Spatiotemporal Model of Firm Growth and Broadband Availability: Evidence from North Carolina,'' Southern Regional Sciences Association (SRSA) Meetings: San Antonio, TX 28 March 2014.
\item ``Attracting Retirees as a Rural Development Strategy: Identifying and Mapping the Potential,'' Southern Regional Sciences Association (SRSA) Meetings: Washington, DC 5 April 2013.
\end{itemize}

\section*{Outreach}

\subsection*{Outreach Reports}

\begin{itemize}
\item \textbf{Dinterman, R.}, and A.L. Katchova, ``\href{https://aede.osu.edu/sites/aede/files/publication_files/2018CAUVProjectionsReport.pdf}{Ohio CAUV Value Projections for 2018}.'' Report, Department of Agricultural, Environmental Economics, The Ohio State University, February 2018.
\item Demko, I., \textbf{R. Dinterman}, M. Marez, and E.C. Jaenicke. ``\href{https://ota.com/sites/default/files/indexed_files/OTATradeReport_10-30-2017.pdf}{U.S. Organic Trade from 2011 to 2016}.'' The Ohio State University, Organic Trade Association and Penn State University, May 2017.
\end{itemize}

% \subsection*{Technical Reports}
% 
% \begin{itemize}
% \item Dinterman, R., and A.L. Katchova, \href{https://aede.osu.edu/about-us/publications/cauv-projections-report-2019}{``CAUV Projections Report 2019.''} Report, Department of Agricultural, Environmental Economics, The Ohio State University, May 2019.
% \item Dinterman, R., and A.L. Katchova, \href{https://aede.osu.edu/sites/aede/files/publication_files/2018CAUVProjectionsReport.pdf}{``Ohio CAUV Value Projections for 2018.''} Report, Department of Agricultural, Environmental Economics, The Ohio State University, February 2018.
% \end{itemize}

\subsection*{Outreach Articles}

\begin{itemize}
\item Dinterman, R., and A.L. Katchova, \href{https://aede.osu.edu/sites/aede/files/publication_files/CAUVProjectionsReport2019.pdf}{``Ohio CAUV Value Projections for 2019 and 2020,''} OSU-AEDE Policy Brief, May 2019.
\item Dinterman, R., and A.L. Katchova, \href{https://www.farmermac.com/wp-content/uploads/The-Feed-Spring-2019.pdf}{``An Update on Farm Bankruptcies,''} Farmer Mac, Spring 2019.
\item Dinterman, R., and A.L. Katchova, \href{https://aede.osu.edu/sites/aede/files/publication_files/2018CAUVProjectionsReport.pdf}{``Ohio CAUV Value Projections for 2018,''} OSU-AEDE Policy Brief, February 2018.
\item Dinterman, R., and A.L. Katchova, \href{https://www.farmermac.com/wp-content/uploads/The-Feed-Spring-2017.pdf}{``Farm Bankruptcies Over Time,''} Farmer Mac, Spring 2017.
\item Dinterman, R., and A.L. Katchova, \href{https://aede.osu.edu/sites/aede/files/publication_files/Farm%20Bankruptcies%20-%20Policy%20Brief.pdf}{``Farm Bankruptcies in the United States,''} OSU-AEDE Policy Brief, April 2017.
\end{itemize}

\subsection*{News Articles}

\begin{itemize}
\item \href{https://aede.osu.edu/sites/aede/files/publication_files/BankruptcyUpdate2019Q2.pdf}{Slight Increase in Farm Bankruptcies through Second Quarter of 2019}, OSU-AEDE, 2019
\item \href{https://aede.osu.edu/news/taxes-farmland-dropping-steadily}{Taxes on Farmland Dropping Steadily}, OSU-AEDE, 2019
\item \href{https://aede.osu.edu/news/cauv-values-agricultural-land-are-expected-decline-112-acre-average}{CAUV Values are Expected to Decline by 11.2\% on Average}, OSU-AEDE, 2018
\item \href{https://aede.osu.edu/news/farm-income-expected-rise}{Farm Income Expected to Rise}, OSU-AEDE, 2017.
\item \href{https://aede.osu.edu/news/bumper-profits-arent-predicted-ohio-farmers-ag-economy-not-repeating-1980s}{Bumper Profits Aren't Predicted for Ohio Farmers but the Ag Economy is not Repeating the 1980s}, OSU-AEDE, 2017.
\item \href{https://aede.osu.edu/news/farm-bankruptcies-could-rise}{Farm Bankruptcies Could Rise}, OSU-AEDE, 2017.
\end{itemize}

\subsection*{Media Mentions}

\begin{itemize}

\item \href{https://www.wksu.org/post/ohio-farm-bankruptcies-stable-despite-flooding-losses#stream/0}{Ohio Farm Bankruptcies Stable Despite Flooding Losses}, WKSU, August 2019.
\item \href{https://radio.wosu.org/post/ohio-farmers-filed-fewest-bankruptcies-midwest#stream/0}{Ohio Farmers Filed Fewest Bankruptcies In Midwest}, WOSU, August 2019.
\item \href{https://www.agweb.com/article/chapter-12-bankruptcies-dont-fully-reveal-the-pain-in-farm-country/}{Chapter 12 Bankruptcies Don't Fully Reveal the Pain in Farm Country}, Farm Journal's AGWEB, May 2019.
\item \href{https://www.agprofessional.com/article/trends-show-chapter-12-bankruptcies-not-rising-alarming-rate}{Trends Show Chapter 12 Bankruptcies Not Rising At An Alarming Rate}, Farm Journal's AGPRO, April 2019.
\item \href{http://investigations.debtwire.com/bitter-harvest-debt-and-the-bankrupting-of-the-american-family-farm/}{Bitter Harvest: Debt and the Bankrupting of the American Family Farm}, Debtwire, March 2019.
\item \href{https://www.politifact.com/truth-o-meter/statements/2019/feb/27/tulsi-gabbard/tulsi-gabbard/}{Fact-checking Tulsi Gabbard on farmers' bankruptcies, median income}, Politifact, February 2019.
\item \href{https://www.politifact.com/punditfact/statements/2019/feb/26/heidi-heitkamp/does-us-have-record-bankruptcies-farm-country/}{Does the U.S. have record bankruptcies in farm country?}, Politifact, February 2019.

\item \href{http://www.nonpareilonline.com/news/politics/national_government/new-law-sponsored-by-chuck-grassley-relieves-a-tax-headache/article_c13b6ee6-d38c-11e7-a679-aff36c8016b4.html}{New law, sponsored by Chuck Grassley, relieves a tax headache for farmers facing hard times}, The Daily Nonpareil, November 2017.
\item \href{http://www.dispatch.com/news/20170921/bumper-profits-arent-in-picture-for-ohio-farmers-experts-say}{Bumper profits aren't in the picture for Ohio farmers, experts say}, The Columbus Dispatch, September 2017.
\item \href{https://www.agweb.com/article/farm-bankruptcies-are-scarce-in-corn-belt-study-finds-naa-nate-birt/}{Farm bankruptcies are scarce in Corn Belt, study finds}, Ag Web, April 2017
\item Farm bankruptcies could rise, \href{https://www.morningagclips.com/farm-bankruptcies-could-rise/}{Morning Ag Clips}, \href{http://www.lancasterfarming.com/market_news/finances/farm-bankruptcies-could-rise/article_21bbfc3f-9e2a-5e25-a737-36a84f140178.html}{Lancaster Farming}, and \href{http://ocj.com/2017/04/farm-bankruptcies-could-rise/}{Ohio's Country Journal and Ohio Ag Net}, April 2017.
\item \href{https://www.agriculture.com/news/business/farm-bankruptcy-rates-are-sure-to-rise-says-analyst}{Farm bankruptcies are sure to rise, says analyst}, Successful Farming at Agriculture.com, February 2017.
\item \href{http://www.newsobserver.com/news/local/community/cary-news/article10235465.html}{Google bringing its high-speed Internet service to the Triangle,} The News \& Observer, January 2015.
\end{itemize}

% \newpage


\section*{R Packages}

\begin{itemize}
\item \href{https://cran.r-project.org/web/packages/usdarnass/}{usdarnass} - An alternative for downloading various USDA data from \href{https://quickstats.nass.usda.gov/}{Quick Stats} through R.
\end{itemize}


\section*{Professional Associations}

\begin{itemize}
\item Awards:
\begin{itemize}
  \item Agricultural, Finance, and Management Outstanding Young Scholar Award 2019 (AAEA).
  \end{itemize}
\item Member:
  \begin{itemize}
  \item Agricultural \& Applied Economics Association (AAEA).
  \item Southern Regional Sciences Association (SRSA).
  \item NC1177 Agricultural Finance and Rural Markets in Transition.
  \end{itemize}
\item Reviewer:
  \begin{itemize}
  \item Agribusiness, Agricultural Economics, Agricultural Finance Review (AFR), American Journal of Agricultural Economics (AJAE), Applied Economic Perspectives and Policy (AEPP), Canadian Journal of Agricultural Economics (CJAE), and Journal of Agricultural and Applied Economics (JAAE).
  \end{itemize}
\item Judge: \href{http://hack.osu.edu/2016/}{HackOHI/O}.
\end{itemize}


\section*{Proficiencies}

\begin{itemize}
\item Expert: R.
\item Advanced: GIS, Git, \LaTeX, Matlab, and SQL.
\item Intermediate: ArcGIS, Microsoft Office, Python, SAS, and Stata.
\end{itemize}


\section*{References}

\begin{multicols}{2}
\begin{itemize}
\item Ani Katchova \\ Associate Professor and \\ Farm Income Enhancement Chair \\ The Ohio State University \\ \href{mailto:katchova.1@osu.edu}{\tt katchova.1@osu.edu} \\ Office: (614) 292-6229
\item Barry K. Goodwin \\ William Neal Reynolds Distinguished Professor \\ North Carolina State University \\ \href{mailto:barry\_goodwin@ncsu.edu}{\tt barry\_goodwin@ncsu.edu} \\ Office: (919) 515-4620

\item Mitch Renkow \\ Professor of Agricultural and \\ Resource Economics \\ North Carolina State University \\ \href{mailto:mitch\_renkow@ncsu.edu}{\tt mitch\_renkow@ncsu.edu} \\ Office: (919) 515-5179
\item Ivan Kandilov \\ Associate Professor of Agricultural and Resource Economics \\ North Carolina State University \\ \href{mailto:ivan\_kandilov@ncsu.edu}{\tt ivan\_kandilov@ncsu.edu} \\ Office: (919) 513-3713
%\item Tamah Morant (Teaching) \\ Associate Dean for Undergraduate Programs, \\ Teaching Associate Professor, Graduate Faculty \\ North Carolina State University \\ \href{mailto:tamah\_morant@ncsu.edu}{\tt tamah\_morant@ncsu.edu} \\ Office: (919) 515-5565
\end{itemize}
\end{multicols}

% \subsection*{Teaching}
% \begin{itemize}
% \item David Hyman \\ Alumni Distinguished Undergraduate Professor of Economics \\ North Carolina State University \\ \href{mailto:david\_hyman@ncsu.edu}{\tt david\_hyman@ncsu.edu} \\ Office: (919) 513-2868
% \item Tamah Morant \\ Economics Graduate Programs Director \\ North Carolina State University \\ \href{mailto:tamah\_morant@ncsu.edu}{\tt tamah\_morant@ncsu.edu} \\ Office: (919) 515-4616
% \end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{http://robertdinterman.com/research/CV\_Dinterman.pdf}}
  \end{footnotesize}
\end{center}

\end{document}